---
title: "bibliometrix package"
author: "Sumit Shinde"
date: "03/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
#Set working Directory 
setwd("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data")


#Install required packages
rm(list = ls())

pklist <- c("tidyverse","bibliometrix","tm","wordcloud")
source("https://fgeerolf.github.io/code/load-packages.R")

```


```{r, eval = FALSE, include=F}
#Attempt to loop over text file names
# for(i in 1:9){
# 
# assign(paste("D.",i,sep=""), readFiles(paste("savedrecs (",i,").txt",sep="")))
# 
# t2 <- paste("D.",i,sep="")
# t1 <- convert2df(t2, dbsource = "isi")
# 

#}
```

```{r, include=F}

D1<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (1).txt")
D2<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (2).txt")
D3<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (3).txt")
D4<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (4).txt")
D5<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (5).txt")
D6<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (6).txt")
D7<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (7).txt")
D8<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (8).txt")
D9<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (9).txt")
D10<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (10).txt")
D11<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (11).txt")
D12<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (12).txt")
D13<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (13).txt")
D14<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (14).txt")
D15<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (15).txt")
D16<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (16).txt")
D17<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (17).txt")
D22<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (22).txt")
D23<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (23).txt")
D24<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (24).txt")
D25<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (25).txt")
D26<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (26).txt")
D27<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (27).txt")
D28<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (28).txt")
D29<- readFiles("C:/Users/sumit/Documents/UCLA/3rd Year/macro chapter/bibliography data/savedrecs (29).txt")


D1<- convert2df(D1, dbsource ="isi")
D2<- convert2df(D2, dbsource ="isi")
D3<- convert2df(D3, dbsource ="isi")
D4<- convert2df(D4, dbsource ="isi")
D5<- convert2df(D5, dbsource ="isi")
D6<- convert2df(D6, dbsource ="isi")
D7<- convert2df(D7, dbsource ="isi")
D8<- convert2df(D8, dbsource ="isi")
D9<- convert2df(D9, dbsource ="isi")
D10<- convert2df(D10, dbsource ="isi")
D11<- convert2df(D11, dbsource ="isi")
D12<- convert2df(D12, dbsource ="isi")
D13<- convert2df(D13, dbsource ="isi")
D14<- convert2df(D14, dbsource ="isi")
D15<- convert2df(D15, dbsource ="isi")
D16<- convert2df(D16, dbsource ="isi")
D17<- convert2df(D17, dbsource ="isi")
D22<- convert2df(D22, dbsource ="isi")
D23<- convert2df(D23, dbsource ="isi")
D24<- convert2df(D24, dbsource ="isi")
D25<- convert2df(D25, dbsource ="isi")
D26<- convert2df(D26, dbsource ="isi")
D27<- convert2df(D27, dbsource ="isi")
D28<- convert2df(D28, dbsource ="isi")
D29<- convert2df(D29, dbsource ="isi")

data <- list(D1,D2,D3,D4,D5,D6,D7,D8,D9,D10,D11,D12,D13,D14,D15,D16,D17,D22,D23,D24,D25,D26,D27,D28,D29)

D <- bind_rows(data)

#Trying to not loose the attributes
# D <- do.call(rbind, unname(data))
# 
# D <- rbind_all(lapply(data,add_rownames))
# 
#rm(D1,D2,D3,D4,D5,D6,D7,D8,D9,D10,D11,D12,D13,D14,D15,D16,D17,D22,D23,D24,D25,D26,D27,D28,D29)

```


```{r, include=F}
d <- D %>% filter(SO== "JOURNAL OF MONETARY ECONOMICS"|
                  SO== "REVIEW OF ECONOMIC DYNAMICS"|
                  SO== "JOURNAL OF MONEY CREDIT AND BANKING"|
                  SO== "AMERICAN ECONOMIC JOURNAL-MACROECONOMICS")

d <- citations(d, sep=";")

d <- as.data.frame(d)

d <- d %>% filter(Source=="J POLIT ECON" | 
                  Source=="Q J ECON" | 
                  Source=="AM ECON REV" | 
                  Source=="ECONOMETRICA" | 
                  Source=="REV ECON STUD") %>%
          filter(Year>1999 & Year<2019) %>% 
          separate(Cited.CR, c("Author","DOI", "b","c"), sep="DOI ", extra = "merge") %>%
          select(-c,-b) %>%
          filter(is.na(DOI)==0) %>%
          rename(DI=DOI) %>%
          mutate(id=1)

D <- D %>% left_join(d,by="DI") %>% filter(!(SO=="ECONOMETRICA" & is.na(id)==1) &
                                           !(SO=="AMERICAN ECONOMIC REVIEW"  & is.na(id)==1) &
                                           !(SO=="QUARTERLY JOURNAL OF ECONOMICS" & is.na(id)==1) &
                                           !(SO=="REVIEW OF ECONOMIC STUDIES" & is.na(id)==1) &
                                           !(SO=="JOURNAL OF POLITICAL ECONOMY" & is.na(id)==1))

rm(d)


```
|

```{r, include=FALSE}
temp2<- D %>% select(PY,AB) %>% 
              mutate(mon.pol=as.numeric(str_detect(AB,"MONETARY")),
                     fis.pol=as.numeric(str_detect(AB,"FISCAL")),
                     crisis=as.numeric(str_detect(AB,"CRISIS")),
                     recession=as.numeric(str_detect(AB,"RECESSION")),
                     bus.cyc=as.numeric(str_detect(AB,"BUSINESS CYCLE")),
                     growth=as.numeric(str_detect(AB,"GROWTH")),
                     banking=as.numeric(str_detect(AB,"BANKING")),
                     friction=as.numeric(str_detect(AB,"FRICTION")),
                     het.agent=as.numeric(str_detect(AB,"HETEROGENOUS AGENT")),
                     model=as.numeric(str_detect(AB,"MODEL")),
                     dsge=as.numeric(str_detect(AB,"DSGE")),
                     rbc=as.numeric(str_detect(AB,"RBC")),
                     housing=as.numeric(str_detect(AB,"HOUSING")),
                     debt=as.numeric(str_detect(AB,"DEBT")),
                     simul=as.numeric(str_detect(AB,"SIMULATION")),
                     calib=as.numeric(str_detect(AB,"CALIBRATION")),
                     c.fact=as.numeric(str_detect(AB,"COUNTER FACTUAL")),
                     reg=as.numeric(str_detect(AB,"REGRESSION")),
                     empiric=as.numeric(str_detect(AB,"EMPIRIC")),
                     r.e=as.numeric(str_detect(AB,"RATIONAL EXPECTATION")),
                     neo.clas=as.numeric(str_detect(AB,"CLASSICAL")),
                     neo.key=as.numeric(str_detect(AB,"KEYNES")),
                     theory=as.numeric(str_detect(AB,"THEORY")),
                     evidence=as.numeric(str_detect(AB,"EVIDENCE")),
                     data=as.numeric(str_detect(AB,"DATA"))) %>%
              group_by(PY) %>%
              summarise(tot.papers=n(),
                        mon.pol=sum(mon.pol, na.rm=TRUE),
                        fis.pol=sum(fis.pol,na.rm=TRUE),
                        crisis=sum(crisis,na.rm=TRUE),
                        recession=sum(recession,na.rm=TRUE),
                        bus.cyc=sum(bus.cyc, na.rm=TRUE),
                        growth=sum(growth, na.rm=TRUE),
                        banking=sum(banking,na.rm=TRUE),
                        friction=sum(friction,na.rm=TRUE),
                        het.agent=sum(het.agent,na.rm=TRUE),
                        model=sum(model, na.rm=TRUE),
                        dsge=sum(dsge,na.rm=TRUE),
                        rbc=sum(rbc,na.rm=TRUE),
                        housing=sum(housing,na.rm=TRUE),
                        debt=sum(debt,na.rm=TRUE),
                        simul=sum(simul, na.rm=TRUE),
                        calib=sum(calib,na.rm=TRUE),
                        c.fact=sum(c.fact,na.rm=TRUE),
                        reg=sum(reg,na.rm=TRUE),
                        empiric=sum(empiric,na.rm=TRUE),
                        r.e=sum(r.e,na.rm=TRUE),
                        neo.clas=sum(neo.clas,na.rm=TRUE),
                        neo.key=sum(neo.key,na.rm=TRUE),
                        theory=sum(theory,na.rm=TRUE),
                        evidence=sum(evidence,na.rm=TRUE),
                        data=sum(data,na.rm=TRUE)) %>%
              mutate(mon.pol=(mon.pol/tot.papers)*100, 
                     fis.pol=(fis.pol/tot.papers)*100, 
                     crisis=(crisis/tot.papers)*100, 
                     recession=(recession/tot.papers)*100,
                     bus.cyc=(bus.cyc/tot.papers)*100, 
                     growth=(growth/tot.papers)*100,
                     banking=(banking/tot.papers)*100, 
                     friction=(friction/tot.papers)*100, 
                     het.agent=(het.agent/tot.papers)*100,
                      model=(model/tot.papers)*100, 
                      dsge=(dsge/tot.papers)*100, 
                      rbc=(rbc/tot.papers)*100,
                      housing=(housing/tot.papers)*100, 
                      debt=(debt/tot.papers)*100,
                     simul=(simul/tot.papers)*100,
                     calib=(calib/tot.papers)*100, 
                     c.fact=(c.fact/tot.papers)*100, 
                     reg=(reg/tot.papers)*100, 
                     empiric=(empiric/tot.papers)*100,
                     r.e=(r.e/tot.papers)*100,
                     neo.clas=(neo.clas/tot.papers)*100,
                     neo.key=(neo.key/tot.papers)*100,
                     theory=(theory/tot.papers)*100,
                     evidence=(evidence/tot.papers)*100,
                     data=(data/tot.papers)*100)
```

## Number of Papers
I have selected top 5 journals: American Economic Review, Econometrica, Journal of Political Economy, Quarterly Journal of Economics, Review of Economic Studies. 

And top 4 macro field journals: Journal of Money, Credit and Banking, Review of Economic Dynamics, Journal of Monetary Economics, American Economic Journal- Macroeconomics. 

The vertical blue line in the graph below higlights year 2008. 


```{r, echo=FALSE, message=FALSE}
#Policy
temp3 <- select(D,PY,SO) %>% 
          group_by(PY,SO) %>% 
          summarise(tot.papers=n()) %>% 
          ungroup%>% 
          mutate(SO=replace(SO,SO=="AMERICAN ECONOMIC JOURNAL-MACROECONOMICS","AEJ-Macro"),
                 SO=replace(SO,SO=="AMERICAN ECONOMIC REVIEW","AER"),
                 SO=replace(SO,SO=="ECONOMETRICA","ECMA"),
                 SO=replace(SO,SO=="JOURNAL OF MONEY CREDIT AND BANKING","JMCB"),
                 SO=replace(SO,SO=="JOURNAL OF POLITICAL ECONOMY","JPE"),
                 SO=replace(SO,SO=="QUARTERLY JOURNAL OF ECONOMICS","QJE"),
                 SO=replace(SO,SO=="REVIEW OF ECONOMIC DYNAMICS","REDyn"),
                 SO=replace(SO,SO=="REVIEW OF ECONOMIC STUDIES","REStud"),
                 SO=replace(SO,SO=="JOURNAL OF MONETARY ECONOMICS","JME")) %>% rename(Journal=SO)
    

ggplot(temp3, aes(PY,tot.papers,color=Journal)) + 
  geom_point(size=0.75) + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1) 

rm(temp3)               
```

## Word Clouds
### Keywords
```{r, echo=FALSE, message=FALSE, warning=FALSE}
corpus <- Corpus(VectorSource(D$DE))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, removeWords, c("elsevier","reserved","rights","by","can"))

tdm <- TermDocumentMatrix(corpus)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word= names(v), freq=v)

wordcloud(d$word,d$freq, random.order=FALSE,max.words=100,colors=brewer.pal(8,"Dark2"))

rm(tdm,m,v,corpus)
```

### Abstract
```{r, echo=FALSE, message=FALSE, warning=FALSE}
corpus <- Corpus(VectorSource(D$AB))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, removeWords, c("elsevier","reserved","rights","by","can","however","increase","paper","use"))

tdm <- TermDocumentMatrix(corpus)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word= names(v), freq=v)

wordcloud(d$word,d$freq, random.order=FALSE,max.words=100,colors=brewer.pal(8,"Dark2"))
```


## Trends

### Policy

```{r, echo=FALSE, message=FALSE}
#Policy
ggplot(gather(select(temp2,PY,mon.pol,fis.pol),`mon.pol`,`fis.pol`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1)
```

### Crisis, Recession, Housing, Debt and Banking

```{r, echo=FALSE, message=FALSE}
ggplot(gather(select(temp2,PY,crisis,recession,housing,debt,banking),`crisis`,`recession`,`housing`,`debt`,`banking`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1)
```

### Business Cyles, Growth

```{r, echo=FALSE, message=FALSE}
ggplot(gather(select(temp2,PY,bus.cyc,growth),`bus.cyc`,`growth`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1)
```


### RBC, DSGE, Simulation, Calibration, Counter-Factural, Regression

```{r, echo=FALSE, message=FALSE}
#methodology   
ggplot(gather(select(temp2,PY,dsge,simul,calib,c.fact,reg,rbc),`rbc`,`dsge`,`simul`,`calib`,`c.fact`,`reg`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1)
```

### Model, Empiric, theory, evidence, data

```{r, echo=FALSE, message=FALSE}
ggplot(gather(select(temp2,PY,model,empiric,evidence,data,theory),`model`,`empiric`,`evidence`,`data`,`theory`,key="trend",value="prop"),aes(PY,prop,color=trend)) +   geom_point() + 
  geom_smooth(se=F)  +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1) 
```              

### NeW-Keysian, Neo-classical 

```{r, echo=FALSE, message=FALSE}
ggplot(gather(select(temp2,PY,neo.clas,neo.key),`neo.clas`,`neo.key`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F) +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1) 
```

### New Modelling Strategies- Friction, Heterogenous Agent, Rational Expectations

```{r, echo=FALSE, message=FALSE}
ggplot(gather(select(temp2,PY,friction,het.agent,r.e),`friction`,`het.agent`,`r.e`,key="trend",value="prop"),aes(PY,prop,color=trend)) + 
  geom_point() + 
  geom_smooth(se=F)  +
  geom_vline(xintercept = 2008, linetype="dotted", color = "blue", size=1)
```

# Bibliometric Analysis
```{r, echo=F}
S <- biblioAnalysis(D, sep=";")
options(width=100)
S <- summary(object = sumary, k = 25, pause = FALSE)
plot(x=sumary, k=25, pause=F)
```




```{r, eval=F, include=F}
CR <- citations(D, field = "article", sep = ";")
topAU <- authorProdOverTime(D, k = 25, graph = TRUE)

# LCR <- localCitations(D, sep = ";")
# LCR$Authors[1:10,]
# LCR$Papers[1:10,]
```


```{r, eval=F, include=F}
# D.sub <- D %>% filter(as.numeric(str_detect(DE,"BUSINESS CYCLE"))==1) %>%
#           select(PT,AU,AF,TI,SO,DE,ID,AB,CR,
#                  NR,TC,Z9,U1,U2,SN,EI,PD,PY,
#                  VL,BP,EP,DI,SC,UT,DA,ER,OI,
#                  RI,HC,CT,CY,CL,HO,PM,SU,IS,
#                  DB,C1,AU_UN,SR_FULL,SR)
# NetMatrix <- biblioNetwork(D, analysis = "coupling", network = "authors", sep = ";")
# 
# net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 100, Title = "Authors' Coupling", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.8,label.n=10,label.cex=F)

NetMatrix <- biblioNetwork(D, analysis = "co-citation", network = "references", sep = ";")


net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)

netstat <- networkStat(NetMatrix)

net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 100, Title = "Authors' Coupling", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.8,label.n=10,label.cex=F)
```